Utilizing Convolution for Obstacle Avoidance during Robotic Manipulator Movement

### 2023-07-21 Articles/ERK/erk.tex
ERK kinematic equations

\todocomment{Preveri pravilnost informacij, dodaj vire, ki potrjujejo informacije.}

\todocomment{preveri podobnost naše metode z metodo: Vector Field Histogram (VFH) }

@@

@@

\todocomment{probably needs shortening \\
			 add equations}

@@

\todocomment{maybe add element-wise convolution equation}

@@

\todocomment{Tukaj bi lahko uporabil D* metodo. Ampak realno je za 4 strani snovi že dovolj.}

@@

\todocomment{-The wall visualization. \\
			 -Line field strenght dx,dy,dz}

>>>>

@@

\begin{equation}
	J^{\dagger} = (J^{T}J)^{-1}J^{T}
	\label{eq:moore_penrose}
\end{equation}

@@

\begin{equation}
	N = (I - J^{\dagger}(q)J(q))
	\label{eq:Null-Space}
\end{equation}

\begin{equation}
	\dot{q} = J^{\dagger}(q) \dot{x}_{ee} + N J^{\dagger}_{poi} \dot{x}_{poi}
	\label{eq:manipulator_kinematics}
\end{equation}

\todocomment{probably needs shortening \\
			 add kinematics equations}

@@

\todocomment{add element-wise convolution equation}

@@

@@

\todocomment{- The wall visualization with robot and wall and "dy beam" and dy arrow. \\
			 - Line field strenght 2D plot dx,dy,dz \\
		 	 - }
